% Enable hyperlinks
\setupinteraction
  [state=start,
  style=,
  color=,
  contrastcolor=]
% make chapter, section bookmarks visible when opening document
\placebookmarks[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][chapter, section]
\setupinteractionscreen[option=bookmark]
\setuptagging[state=start]

% use microtypography
\definefontfeature[default][default][script=latn, protrusion=quality, expansion=quality, itlc=yes, textitalics=yes, onum=yes, pnum=yes]
\definefontfeature[smallcaps][script=latn, protrusion=quality, expansion=quality, smcp=yes, onum=yes, pnum=yes]
\setupalign[hz,hanging]
\setupitaliccorrection[global, always]
\setupbodyfontenvironment[default][em=italic] % use italic as em, not slanted
\usemodule[simplefonts]
\setmainfontfallback[DejaVu Serif][range={greekandcoptic, greekextended}, force=yes, rscale=auto]
\setupwhitespace[medium]

\setuphead[chapter]            [style=\tfd,header=empty]
\setuphead[section]            [style=\tfc]
\setuphead[subsection]         [style=\tfb]
\setuphead[subsubsection]      [style=\bf]
\setuphead[subsubsubsection]   [style=\sc]
\setuphead[subsubsubsubsection][style=\it]

\setuphead[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm, alternative=hanging]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupthinrules[width=15em] % width of horizontal rules


\starttext

\section[tiny-oh]{Tiny Oh}

你可能需要我的\useURL[url1][http://tinyslik.coding.me/resume][][中文简历]\from[url1]
Graphics Developer -----------------------

\startitemize[packed]
\item
  Phone:
  \useURL[url2][tel://86-15861657693][][86-15861657693]\from[url2]
\item
  Email:
  \useURL[url3][mailto:tinysilk@hotmail.com][][tinysilk@hotmail.com]\from[url3]
\item
  Blog out of China:
  \useURL[url4][http://tinyslik.github.io][][tinyslik.github.io]\from[url4]
\item
  Blog in China:
  \useURL[url5][http://tinyslik.coding.me][][tinyslik.coding.me]\from[url5]
\item
  Github:
  \useURL[url6][http://github.com/TinySlik][][TinySlik]\from[url6]
\stopitemize

\subsection[summary]{Summary}

I am an young graphics developer who has 4 years program experience.
successful \$1MM+ projects. I am passionate about building high quality
apps I am able to execute end-to-end on a product or project.

\subsection[specialties]{Specialties}

Authoring great user experiences with openGL(include ES and web),
HTML5+CSS, C/C++ ,Lua; use cocos2d-x,uinity3d for a lone time .

\subsection[experience]{Experience}

\subsubsection[cc-developer-at-mochang-inc]{{\bf C/C++ Developer} at
\useURL[url7][https://www.mochang.net/][][MoChang inc]\from[url7]}

{\em January 2014 - July 2015}

In the company mainly engaged in cocos2d-x game production and
maintenance work, the use of C + + reconstruction code, configure more
functional modules, learning a lot of C + + basic syntax and table
driver, plug-in architecture and other commonly used language design
patterns. As a result of my work in biotechnology, this is a challenge.
In this company I worked for a year, shelved some of the more simple
children's games, a large number of functional modules reuse and
maintenance.

These are languages, tools, and practices to which I have had exposure
over the past 4 years or so. Those things which enjoy routine usage in
my daily work are denoted with a \high{†} symbol.

\subsubsection[programming-languages]{Programming Languages}

\startitemize[packed]
\item
  \useURL[url8][][][C/C++]\from[url8]\high{†}
\item
  \useURL[url9][][][Lua]\from[url9]\high{†}
\item
  \useURL[url10][][][javaScript]\from[url10]\high{†}
\item
  \useURL[url11][][][java]\from[url11]
\item
  \useURL[url12][][][object-C]\from[url12]
\item
  \useURL[url13][][][jason]\from[url13]\high{†}
\item
  \useURL[url14][][][xml]\from[url14]\high{†}
\item
  \useURL[url15][][][C\#]\from[url15]
\item
  \useURL[url16][][][shader]\from[url16]\high{†}
\stopitemize

\subsubsection[markuptemplating-languages-preprocessors]{Markup/Templating
Languages & Preprocessors}

\startitemize
\item
  \useURL[url17][http://www.w3.org/Style/CSS/Overview.en.html][][CSS]\from[url17]\high{†}
\item
  \useURL[url18][http://developers.whatwg.org][][HTML]\from[url18]\high{†}
\item
  \useURL[url19][http://daringfireball.net/projects/markdown][][Markdown]\from[url19]\high{†}
\item
  \useURL[url20][][][XML]\from[url20]
\item
  \useURL[url21][][][jason]\from[url21]
\item
  \useURL[url22][][][http]\from[url22]
\item
  \subsubsection[frameworks-apis]{Frameworks & APIs}
\item
  \useURL[url23][][][OpenGL
  （web,ES,glut,glew\ldots{}）]\from[url23]\high{†}
\item
  \useURL[url24][][][Boost]\from[url24]
\item
  \useURL[url25][][][Cocos2d-x]\from[url25]\high{†}
\item
  \useURL[url26][][][Uinity3d]\from[url26]
\item
  \useURL[url27][][][hexo]\from[url27]\high{†}
\stopitemize

\subsubsection[software-tools]{Software & Tools}

\startitemize[packed]
\item
  \useURL[url28][http://developer.apple.com][][Apple Xcode]\from[url28]
\item
  \useURL[url29][http://git-scm.com][][Git]\from[url29]\high{†}
\item
  \useURL[url30][http://atlassian.com/software/jira][][JIRA]\from[url30]\high{†}
\item
  \useURL[url31][http://apple.com/macosx][][Mac OS
  X]\from[url31]\high{†}
\item
  \useURL[url32][http://mysql.com][][MySQL]\from[url32]
\item
  \useURL[url33][http://wiki.nginx.org][][Nginx]\from[url33]
\item
  \useURL[url34][http://johnmacfarlane.net/pandoc][][Pandoc]\from[url34]
\item
  \useURL[url35][http://www.sublimetext.com][][Sublime Text]\from[url35]
\item
  \useURL[url36][http://svn.apache.org][][Subversion]\from[url36]
\item
  \useURL[url37][http://ubuntu.com][][Ubuntu Linux]\from[url37]
\item
  \useURL[url38][http://www.vim.org][][Vim]\from[url38]\high{†}
\item
  \useURL[url39][http://jetbrains.com/webstorm][][WebStorm]\from[url39]
\item
  \useURL[url40][http://www.zsh.org][][zsh]\from[url40]\high{†}
\item
  \useURL[url41][][][source tree]\from[url41]
\item
  \useURL[url42][][][VisualStudio]\from[url42]\high{†}
\item
  \useURL[url43][][][AndroidStudio]\from[url43]
\item
  \useURL[url44][][][grub/grub2]\from[url44]
\item
  \useURL[url45][][][doxygen]\from[url45]
\item
  \useURL[url46][][][latex]\from[url46]
\stopitemize

\subsection[education]{Education}

{[}YangZhou University{]}, 2008 - 2012

\subsection[interests]{Interests}

\startitemize[packed]
\item
  Being a dad and spending time with my family
\item
  Playing \useURL[url47][http://boardgamegeek.com/user/smtudor][][board
  and card games]\from[url47] (and video games, too)
\item
  Making and listening to
  \useURL[url48][http://www.rdio.com/people/smtudor][][music]\from[url48]
\item
  Watching and contributing to Open Source Software
\stopitemize

\subsection[download]{Download}

You may need my resume in

\useURL[url49][https://github.com/TinySlik/resume/raw/master/resume.docx][][doc]\from[url49]

\useURL[url50][https://github.com/TinySlik/resume/raw/master/resume.pdf][][pdf]\from[url50]

\useURL[url51][https://github.com/TinySlik/resume/raw/master/resume.epub][][epub]\from[url51]

Thank you for your watching.

©2016 \useURL[url52][http://tinyslik.github.io/resume][][Tiny
Wu]\from[url52]. All rights reserved. Direct contact only desired
(no~recruiters~please).

\stoptext
